---
title: "Readme"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

In order to build the site, you should install some packages : blogdown, leaflets and magrittr.
You should also install Hugo.

```{r}
devtools::install_deps(upgrade="never")
blogdown::install_hugo()

```


The you need these commands to build the site, add contents and build new posts :

```{r}
blogdown::new_site()

blogdown::new_content("content.Rmd")

blogdown::new_post("Title", ext = 'Rmd')

```
When adding a new content, in the config.toml file you should add

```{r}
[[menu.main]]
    name = "New_content"
    url = "/new_content/"
```


We modified some things :

* Added an images folder in static and put our icon in it

* The logo in config.toml

```{r}
    url = "Image_MEE.png"
```

* The icon in config.toml

```{r}
# path to the favicon, under "static"
    favicon = "Image_MEE.png"
```

* The path of the posts folder in config.toml

```{r}
name = "Editions"
    url = "/post" 
```


